Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
stuff

Let $S(P_t)$ be the build status returned from TravisCI when run on $P_t$.
It can be either $Pass$ or $Err$. We define shorthand $S(P_{t,t+1}) = PE$ to 
state that the program was compiling before and now it does not:
\begin{align*}
  S(P_{t,t+1}) = PE :\Leftrightarrow S(P_t)=Pass \land S(P_{t+1})=Err 
\end{align*}

We now consider both incorrect and correct files in the training set 
and so must introduce the \textit{general boundary}.
The general boundary is the dual of the specific boundary, and is the most relaxed requirement for a positive classification.
We denoted specific boundary as the set of necessary relations $Nec$, and now denote the general boundary as the set of breaking relations $Br$.
With this notation, we can formally express the requirement that the program summary is sufficiently detailed.
\begin{align}
  \forall S(P_t)=Err, \exists r \in M(P_t), r \in Br \label{eq:E1}
\end{align}

From the above we know that if a build is erroring, then there must exist at least one error.
We can also know that if a build is passing, then there must not exist any errors.
That is, the model of a passing commit must not contain any rules which are breaking.
Note we are not, however, guaranteed that any rules from a passing commit are necessary.
\begin{align}
  S(P_t) = Err \implies \exists r \in  M (P_t), r \in Br \label{eq:E}\\
  S(P_t) = Pass \implies \forall r \in  M (P_t), r \notin Br \label{eq:P}
\end{align}

%While Eq. \ref{eq:E} and \ref{eq:P} might build a basic model, they will do not capture all of the available knowledge.
%The key insight is that 
Additionally, when we commit a break ($PE$), we can localize the error to one of the relations that changed.
Either we removed something that was necessary, or added something that was breaking.
Note that this is an inclusive disjunction, since a erroring commit can break multiple things at once.
Expressed formally, where $\setminus$ is the set difference, that is:
\begin{align}
  S(P_{t,t+1}) &= PE \implies \nonumber \\
  \exists& r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \nonumber \\
  \lor \ \exists& r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br \label{eq:PE}
\end{align}

We then can combine \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} with
conjunctions and ask a SMT solver for a model satisfying the formula.
The resulting model will be the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.

>>>>

Let $S(P_t)$ be the build status returned from TravisCI when run on $P_t$.
It can be either $Pass$ or $Err$. We define shorthand $S(P_{t,t+1}) = PE$ (also called a break state), to 
express that the program was compiling before and now it does not:
\begin{align*}
  S(P_{t,t+1}) = PE :\Leftrightarrow S(P_t)=Pass \land S(P_{t+1})=Err 
\end{align*}

If executing a TravisCI file fails, then there must exist at least one rule that is
causing that error. Similarly, if a build is passing, then there must not exist any error.
That is, the model of a passing commit must not contain any breaking rules.
Note we are not, however, guaranteed that any rules from a passing commit are necessary.
\begin{align}
  S(P_t) = Err \Rightarrow \exists r \in  M (P_t), r \in Br \label{eq:E}\\
  S(P_t) = Pass \Rightarrow \forall r \in  M (P_t), r \notin Br \label{eq:P}
\end{align}

%While Eq. \ref{eq:E} and \ref{eq:P} might build a basic model, they will do not capture all of the available knowledge.
%The key insight is that 
Additionally, when we commit a break ($PE$), we can localize the error to one of the relations that changed.
Either we removed something that was necessary, or added something that was breaking.
Note that this is an inclusive disjunction, since a erroring commit can break multiple things at once.
Expressed formally, where $\setminus$ is the set difference, that is:
\begin{align}
  S(P_{t,t+1}) &= PE \Rightarrow \nonumber \\
  \exists& r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \nonumber \\
  \lor \ \exists& r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br \label{eq:PE}
\end{align}

We then create a conjunction of \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} with
conjunctions and invoke an SMT solver to find a model for that formula.
The resulting model will define sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.

We also believe that this approach will work in practice since travis.yml files are relatively small and changes in the files are often at most 1-2 lines.
